CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-28 codecheck-paper.tex
update grant info for Daniel

This work was financially supported by the UK Software
Sustainability Institute and a Mozilla Science mini grant.

@@

We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison, Giuliano
Maciocci (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (Gigascience) Andrew Hufton (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang developed code and example certificates.

>>>>

This work was financially supported by the UK Software
Sustainability Institute and a Mozilla Science mini grant.
DN is supported by grant \href{https://gepris.dfg.de/gepris/projekt/415851837}{PE~1632/17-1} from the German Research Foundation (DFG).

@@

We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison, Giuliano
Maciocci (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (GigaScience), and Andrew Hufton (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang developed code and example certificates.
